Exact Phylodynamics via Structured Markov Genealogy Processes

### 2023-08-10 ms.Rnw
update

\title[Exact Phylodynamics]{Exact Phylodynamics via Structured Markov Genealogy Processes}
\author[King]{Aaron~A.~King}
\address{
  A.~A.~King,
  Department of Ecology \& Evolutionary Biology,
  Center for the Study of Complex Systems, and
  Department of Mathematics,
  University of Michigan,
  Ann Arbor, MI 48109 USA
}
\email{kingaa@umich.edu}
\urladdr{\href{https://kinglab.eeb.lsa.umich.edu/}{https://kinglab.eeb.lsa.umich.edu/}}
\author[Lin]{Qianying Lin}
\address{
  Q.-Y. Lin,
  Theoretical Biology and Biophysics,
  Los Alamos National Laboratory,
  Los Alamos, NM XXXXX USA
}
\author[Ionides]{Edward~L.~Ionides}
\address{
  E.~L.~Ionides,
  Department of Statistics
  University of Michigan,
  Ann Arbor, MI 48109 USA
}
\date{\today}

>>>>

\title[Exact Phylodynamics]{Exact Phylodynamics via Structured Markov Genealogy Processes}
\author[King]{Aaron~A.~King}
\address{
  A.~A.~King,
  Department of Ecology \& Evolutionary~Biology,
  Center for the Study of Complex~Systems, and
  Department of Mathematics,
  University of Michigan,
  Ann~Arbor, MI~48109~USA\\
  Santa~Fe~Institute,
  1399 Hyde~Park~Road,
  Santa~Fe, NM~87501~USA
}
\email{kingaa@umich.edu}
\urladdr{\href{https://kinglab.eeb.lsa.umich.edu/}{https://kinglab.eeb.lsa.umich.edu/}}
\author[Lin]{Qianying~Lin}
\address{
  Q.-Y.~Lin,
  Theoretical Biology and Biophysics,
  Los~Alamos National Laboratory,
  Los~Alamos, NM~87545~USA
}
\author[Ionides]{Edward~L.~Ionides}
\address{
  E.~L.~Ionides,
  Department of Statistics
  University of Michigan,
  Ann~Arbor, MI~48109~USA
}
\date{\today}
